LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-12-12 main.tex
Shorten unambiguous variable names

\begin{figure}
\begin{center}
\setlength\figurewidth{.75\textwidth}
\input{graphics/double_gyre/poincare_return_map.tikz}
\end{center}
\caption{Example of a Poincare map obtained for an elliptic LCS. The abscissa, $s$, represents distance along Poincare section. The ordinate, $p(s) - s$, represents distance of Poincare orbit return point from initial position. Circle markers indicate closed orbit positions. The filled circle indicates the outermost fixed point of the Poincare map, marking the intersection of a coherent Lagrangian vortex boundary with the Poincare section.}
\label{f:Poincare return map}
\end{figure}

@@

\begin{figure}
\centering
\setlength\figurewidth{.875\textwidth}
\import{graphics/double_gyre/}{elliptic_lcs_convergence_500.tikz}
\import{graphics/double_gyre/}{elliptic_lcs_convergence_750.tikz}
\import{graphics/double_gyre/}{elliptic_lcs_convergence_1000.tikz}
\caption{Convergence of closed $\lambda$-lines for increasing main-grid resolution in the double-gyre. The outermost closed $\lambda$-line (bold green line) is the vortex boundary. Top: $500 \times 250$, middle: $750 \times 375$, bottom: $1000 \times 500$.}
\label{f:double gyre lambda LCS convergence}
\end{figure}

@@

\begin{figure}
\centering
\setlength\figurewidth{.8\textwidth}
\import{graphics/double_gyre/}{elliptic_repelling_lcs_details.tikz}
\import{graphics/double_gyre/}{elliptic_attracting_lcs_details.tikz}
\caption{
LCSs in the double gyre.
Resolution is $500 \times 250$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00$ and $1.04$ for the left and the right gyre.
$\lambda \in [0.93,1.07]$, $\Delta\lambda = 0.01$.
}
\label{f:double gyre lambda hyperbolic LCS}
\end{figure}

@@

\begin{figure}
\centering
\setlength\figurewidth{.775\textwidth}
\import{graphics/bickley_jet/}{elliptic_repelling_lcs_details.tikz}
\import{graphics/bickley_jet/}{elliptic_attracting_lcs_details.tikz}
\caption{
LCSs in the Bickley jet.
Resolution is $500 \times 200$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda$ values of elliptic LCSs from left to right are [0.95,\,0.80,\,0.94,\,0.80,\,0.94], $\lambda \in [0.80,1.20]$, $\Delta\lambda = 0.01$.
}
\label{f:Bickley jet LCS}
\end{figure}

@@

\begin{figure}
\begin{center}
\setlength\figurewidth{.85\textwidth}
\import{graphics/ocean_dataset/}{elliptic_repelling_lcs.tikz}
\import{graphics/ocean_dataset/}{elliptic_attracting_lcs.tikz}
\end{center}
\caption{
LCSs in the ocean velocity data from satellite altimetry.
Resolution is $400 \times 400$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00, 1.08, 0.94, 0.90, 1.06$.
}
\label{f:ocean dataset LCS}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\setlength\figurewidth{.75\textwidth}
\import{graphics/double_gyre/}{poincare_return_map}
\end{center}
\caption{Example of a Poincare map obtained for an elliptic LCS. The abscissa, $s$, represents distance along Poincare section. The ordinate, $p(s) - s$, represents distance of Poincare orbit return point from initial position. Circle markers indicate closed orbit positions. The filled circle indicates the outermost fixed point of the Poincare map, marking the intersection of a coherent Lagrangian vortex boundary with the Poincare section.}
\label{f:Poincare return map}
\end{figure}

@@

\begin{figure}
\centering
\setlength\figurewidth{.875\textwidth}
\import{graphics/double_gyre/}{elliptic_lcs_500}
\import{graphics/double_gyre/}{elliptic_lcs_750}
\import{graphics/double_gyre/}{elliptic_lcs_1000}
\caption{Convergence of closed $\lambda$-lines for increasing main-grid resolution in the double-gyre. The outermost closed $\lambda$-line (bold green line) is the vortex boundary. Top: $500 \times 250$, middle: $750 \times 375$, bottom: $1000 \times 500$.}
\label{f:double gyre lambda LCS convergence}
\end{figure}

@@

\begin{figure}
\centering
\setlength\figurewidth{.8\textwidth}
\import{graphics/double_gyre/}{elliptic_repelling_lcs}
\import{graphics/double_gyre/}{elliptic_attracting_lcs}
\caption{
LCSs in the double gyre.
Resolution is $500 \times 250$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00$ and $1.04$ for the left and the right gyre.
$\lambda \in [0.93,1.07]$, $\Delta\lambda = 0.01$.
}
\label{f:double gyre lambda hyperbolic LCS}
\end{figure}

@@

\begin{figure}
\centering
\setlength\figurewidth{.775\textwidth}
\import{graphics/bickley_jet/}{elliptic_repelling_lcs}
\import{graphics/bickley_jet/}{elliptic_attracting_lcs}
\caption{
LCSs in the Bickley jet.
Resolution is $500 \times 200$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda$ values of elliptic LCSs from left to right are [0.95,\,0.80,\,0.94,\,0.80,\,0.94], $\lambda \in [0.80,1.20]$, $\Delta\lambda = 0.01$.
}
\label{f:Bickley jet LCS}
\end{figure}

@@

\begin{figure}
\begin{center}
\setlength\figurewidth{.85\textwidth}
\import{graphics/ocean_dataset/}{elliptic_repelling_lcs}
\import{graphics/ocean_dataset/}{elliptic_attracting_lcs}
\end{center}
\caption{
LCSs in the ocean velocity data from satellite altimetry.
Resolution is $400 \times 400$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00, 1.08, 0.94, 0.90, 1.06$.
}
\label{f:ocean dataset LCS}
\end{figure}
